Adding Interactivity to Static Rmarkdown Documents

### 2017-10-31 02_rmarkdown-interactivity/post.Rmd
lab post progress

@@

- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host. This can be too much overhead for smaller tasks.
- **Non-HTML Rmarkdown outputs** aren't very interactive. Text, plots and other outputs are statically assembled at runtime and the document stays that way.
- **HTML R markdown outputs** are a nice comprimise. They support superficially interactive elements (tooltips, action filtering) through HTML widgets **AND** if you know a few tricks interactivity can be signficantly enhanced. That's the topic of this post!

@@

# Generate Data

@@

```{r}
library(dplyr)
library(tidyr)
library(highcharter)

@@

# Plot Data

@@

hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
  hc_elementId(id = "static_graph") %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(
    title = list(text = "Value")
  ) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities")

@@

   df %>%
    filter(distribution == !!var) %>% # Tidy Evaluation
    mutate(
      js_pair = paste0("[", value, "," , density %>% round(6), "]")
    ) %>%
    pull(js_pair) %>% # Just found this function, handy!
    return()

@@

   df %>%
    filter(distribution == !!var) %>% # Tidy Evaluation
    arrange(value) %>%
    mutate(
      cdf = cumsum(density),
      js_pair = paste0("[", value, "," , cdf %>% round(4), "]")
    ) %>%
    pull(js_pair) %>% # Just found this function, handy!
    return()

>>>>

```{r}
# Knitr Options
knitr::opts_chunk$set(warning=FALSE, message=FALSE, strip.white = FALSE)

@@

- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host as well as codifying a decent amount of interactivity logic in the shiny syntax. This can be too much overhead for smaller tasks.
- **Non-HTML Rmarkdown outputs** aren't very interactive. Text, plots and other outputs are statically assembled at runtime and the document stays that way.
- **HTML R markdown outputs** are a nice comprimise. They support superficially interactive elements (tooltips, action filtering) through HTML widgets **AND** if you know a few tricks interactivity can be signficantly enhanced. That's the topic of this post!

@@

# Example

@@

**Generate Data**
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(highcharter)

@@

Using `highcharter` we'll plot the densities of these 3 distributions.

**Plot Data**
```{r}

@@

hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
  hc_elementId(id = "static_graph") %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(height = 500) %>%
  hc_xAxis(title = list(text = "Value")) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities")

@@

   df %>%
    filter(distribution == !!var) %>% # Tidy Evaluation
    mutate(
      js_pair = paste0("[", value, "," , density %>% round(6), "]")
    ) %>%
    pull(js_pair) %>% # Extract column as vector
    return()

@@

   df %>%
    filter(distribution == !!var) %>% # Tidy Evaluation
    arrange(value) %>%
    mutate(
      cdf = cumsum(density),
      js_pair = paste0("[", value, "," , cdf %>% round(4), "]")
    ) %>%
    pull(js_pair) %>% # Extract column as vector
    return()
